Algorithm explanation

### 2013-09-26 article/experiment.tex
Time

>>>>

\begin{center}
  \begin{tabular}{ | l || c | c | c | l || c | c | }
\hline
Name & gchi & yhorn & \multirow{25}{*}{Defenders} & Name & gchi & yhorn \\ \hline
ack & 1 & 1 & fold_fun_list & 2 & 99 \\ \hline
a-copy-print & 6 & 99 & fold_left & 2 & 2 \\ \hline
a-dotprod & 4 & 4 & fold_right & 2 & 2 \\ \hline
a-init & 99 & 7 & harmonic & 1 & 1 \\ \hline
bcopy & 3 & 3 & hors & 1 & 1 \\ \hline
bcopy-without-size & 4 & 4 & hrec & 1 & 2 \\ \hline
copy_intro & 2 & 99 & inc & 1 & 1 \\ \hline
dotprod_ & 4 & 4 & isnil & 2 & 2 \\ \hline
enc-rev_accum & 2 & 4 & iter & 1 & 1 \\ \hline
enc-rev_append & 5 & 99 & length & 2 & 4 \\ \hline
enc-zip & 2 & 2 & map & 1 & 1 \\ \hline
enc-zip_map & 2 & 99 & mc91 & 2 & 2 \\ \hline
enc-zip_map2 & 4 & 99 & mem & 3 & 3 \\ \hline
enc-zip_unzip & 2 & 99 & mult & 3 & 4 \\ \hline
enc-zip2 & 2 & 99 & nth & 3 & 99 \\ \hline
enc-zipmap & 4 & 99 & nth0 & 3 & 2 \\ \hline
exc-fact & 2 & 3 & queen & 3 & 4 \\ \hline
fact_exn & 2 & 3 & rec_error & 2 & 99 \\ \hline
fact_notpos & 2 & 2 & recursive & 1 & 2 \\ \hline
fact_notpos-e & 1 & 1 & repeat & 2 & 2 \\ \hline
fib & 2 & 99 & sigma_sum & 3 & 3 \\ \hline
file & 6 & 99 & sum & 1 & 1 \\ \hline
file1 & 1 & 1 & twice_rec & 99 & 3 \\ \hline
 &  &  & zip & 3 & 2 \\ \hline
\end{tabular}
\end{center}
